003_ftx_mining.Rmd

### 2020-06-14 analysis/003_cr_xml_fetch.Rmd
invoice data

```{r}
tt <- plyr::llply(sample(elsevier_tdm$URL, 10), .f = purrr::safely(elsevier_parse), .progress = "text")
```

>>>>

```{r}
tt <- plyr::llply(els_hybrid$URL, .f = purrr::safely(elsevier_parse), .progress = "text")
tt_df <- purrr::map_df(tt, "result")
write_csv(tt_df, here::here("data", "invoice_df.csv"))
```
